A holomorphic approach to membranes and fivebranes

### 2022-08-02 fivebranes/twisted.tex
update

\documentclass[11pt]{amsart}%
%
%%\usepackage{../macros-master}
\usepackage{macros-fivebrane}

%
\begin{document}
%

\section{Twists in dimensions eleven, six, and three}

@@

Eleven-dimensional supersymmetry admits two inequivalent classes of twists characterized by the dimension of the subspace of translations spanned by the image of $Q$.
\begin{itemize}
\item 
The minimal twist. 
This twist leaves six real directions invariant and is preserved by the subgroup $SU(5)$ of the Lorentz group. 
\item 
The non-minimal twist. 
This twist leaves nine real directions invariant and is preserved by the subgroup $SU(2) \times G_2$ of the Lorentz group. 
\end{itemize}

@@

The eleven-dimensional theory exists on any manifold which is locally of the form 
\[
S \times X 
\] 
where $X$ is a Calabi--Yau fivefold and $S$ is a real oriented smooth one-dimensional manifold.
More generally, the eleven-dimensional theory can be constructed on any eleven-manifold equipped with a transversely holomorphic foliation which is equipped with an appropriate holomorphic volume form on the leaves of the foliation.

In the first few sections we recall the fields and equations of motion of this eleven-dimensional theory.

@@

To begin this section we highlight some of the important features of the eleven-dimensional model considered in \cite{RSW}. 
Let's first consider the case that the eleven-dimensional manifold is of the form $S \times X$, where $X$ is a Calabi--Yau fivefold.
We let $\T_X$ stand for the holomorphic tangent bundle of $X$ and $\Bar{\T}_X$ its complex conjugate.
The complexified tangent bundle of the eleven-manifold $S \times X$ decomposes as
\[
\T_S \oplus \T_X \oplus \Bar{\T}_X 
\]
where $\T_S$ is the complexified tangent bundle of the smooth one-manifold $S$.
Locally, we choose coordinates $(t;z,\zbar)$ where $t$ is a smooth coordinate for $S$ and $z$ is a holomorphic coordinate for $X$.

Before giving a full description of the fields and equations of motion wrapped up into the BV formalism, we give an explicit description of the equations of motion and gauge symmetries.

One of the primary fields of eleven-dimensional supergravity describes deformations of the metric $g$.
Since we work in a background which has $SU(5)$ holonomy we can take the background metric on $S \times X$ to be the product of the flat metric on $S$ with a Calabi--Yau metric $g_{CY}$ on $X$.

Deformations of the background metric which survive the twist can be identified with Beltrami differentials, that is, sections of 
\[
\Bar{\T}_X^* \otimes \T_X \cong \Bar{\T}^*_X \otimes \Bar{\T}_X^* 
\]
which we will denote by $\mu$. 
In local holomorphic coordinates $\mu$ admits a description like
\[
\mu^{\Bar{i}}_j (t;z,\zbar) \d \zbar_{\Bar{i}} \otimes \del_{z_j} .
\]
More generally, the fields of this model include sections of the holomorphic tangent bundle with coefficients in Dolbeault forms of arbitrary Dolbeault type, which we can write in superfield notation as 
\[
\mu = \mu^{\Bar{I}}_j (t;z,\zbar) \d \zbar_{\Bar{I}} \otimes \del_{z_j}
\]
where there is a sum over the multi-index $\Bar{I}$. 
In this notation, the component of the field $\mu$ is {\em odd} if $|I|=0,2,4$ is even and {\em even} if $|I| = 1,3,5$ is odd.
In particular we have odd fields $\mu_j(t;z,\zbar) \del_{z_j}$ which play the role of ghosts for infinitesimal changes of coordinates.
We will see that the equations of motion dictate that we only see changes of holomorphic coordinates.

The field $\mu$ satisfies a condition that it be {\em divergence-free} for the Calabi--Yau structure on the fivefold~$X$. 
This means that it is required to satisfy the condition 
\beqn
\div \mu = 0
\eeqn
where $\div(-)$ is the divergence with respect to the holomorphic volume form $\Omega$ on $X$.
In the BV formalism one can encode this by introducing another field, but for the sake of discussion we omit that approach for now.
Another piece of the equations of motion for~$\mu$ dictate that it be locally constant along~$S$.

@@

One of the other bosonic fields of eleven-dimensional supergravity is a three-form that we denote by~$\sf C$.
In the BV formalism we see all types of differential forms corresponding to a tower of ghosts for this $C$-field together with antifields and antighosts.

On $S \times X$ the space of complex-valued differential forms decomposes into de Rham--Dolbeault forms as in
\[
\oplus_{k,p,q} \Omega^k(S) \otimes \Omega^{p,q}(X) .
\]
We refer to the homogenous pieces as the space of $(k;p,q)$ forms, these admit local presentations as
\[
\sum_{P,Q} f_{PQ} (t;z,\zbar) \d z_P \d \zbar_Q + \sum_{P',Q'} g_{P'Q'}(t;z,\zbar) \d t \d z_{P'}\d \zbar_{Q'} 
\]
where the first sum is over tuples $P=(p_1,p_2,p_3),Q=(q_1,q_2,q_3)$.
%The second sum is over tuples $P',Q'$ such that $\sum_i (p_i'+q_i') = 2$.

In the minimal twist only forms with $p_i ,p_i'\leq 1$ survive. 
Thus, we have as part of the complex of fields in the twisted theory
\[
\left(\oplus_{k,q} \Omega^k(S) \otimes \Omega^{0,q}(X)\right) \oplus 
\left(\oplus_{k',q'} \Omega^{k'}(S) \otimes \Omega^{1,q'}(X)\right) .
\]
We denote a general (non-homogenous) element in the first summand by $\beta$ and an element in the second summand by $\gamma$.
When we want to be specific by the form type we use the notation $\beta^{k;q}(t;z,\zbar)$ for the $(k;0,q)$ component of the three-form and $\gamma^{k;q}(t;z,\zbar)$ for the $(k;1,q)$ component of the three-form.
Fields $\beta^{k;q}$ with $k+q = $even are {\em odd} and fields $\gamma^{k;q}$ with $k+q = $odd are {\em even} fields.

The most important equation of motion of the eleven-dimensional theory involves both the fields $\mu$ and $\gamma$. 
When $\div \mu = 0$ it takes the form
\beqn\label{eqn:eom2}
\dbar \mu + \frac12 [\mu,\mu] = \del \gamma \del \gamma .
\eeqn
Because of the term on the right hand side this equation is not exactly the usual Beltrami equation for deformations of complex structures.

The theory also enjoys the following gauge symmetries.
First, for any 
\brian{finish}
%Along $S$, $\beta$ and $\gamma$ behave like abelian gauge fields.
%Thus, locally we can assume that the $\Omega^1(S)$ components are exact and the $\Omega^0(S)$ components are locally constant.

@@

We move on to give a complete description of our eleven-dimensional model within the Batalin--Vilkovisky (BV) formalism.
This amounts to introducing antifields and antighosts to the fields and ghosts that we have just described.
One of the key structures is the graded skew-symmetric pairing between fields and antifields (ghosts and antighosts).
Once such a pairing $\omega_{BV}$ is introduced, one can opt to describe solutions to the equations of motion as Maurer--Cartan elements of a certain sheaf of ($\Z/2$-graded) $L_\infty$ algebras on $X \times S$.

@@

The $L_\infty$ structure on the sheaf of holomorphic sections of $L_X$ is described as follows. 
First, $\d = [-]_1$, the differential, is simply given by 
\begin{align*}
\d \beta & = \del \beta \in \Omega^1_X \subset L_{X,-} \\
\d \mu & = \div \mu \in \cO_X \subset L_{X, -}
\end{align*}
and $\d \gamma = \d \nu = 0$. 
For $k \geq 2$ the general formula for the $k$-ary brackets is 
\begin{align*}
[\nu_1, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \div(\nu_1 \cdots \nu_k \mu_1 \wedge \mu_2) \\
[\nu_1,\ldots, \nu_{k-3}, \mu_1,\mu_2,\gamma]_k & = \nu_1 \cdots \nu_{k-3} (\mu \wedge \mu') \vee \del \gamma .\\
[\nu_1,\ldots,\nu_{k-2}, \mu, \gamma]_k & = \nu_1 \cdots \nu_{k-2} \mu \vee \del \gamma .
\end{align*}
In \cite{RSW} it is shown that this endows $L_{X}$ with the structure of a sheaf of $\Z/2$ graded $L_\infty$ algebras.
There is a sub sheaf given by the sections $\mu$ and $\nu$ which is $L_\infty$-equivalent to the sheaf of holomorphic divergence-free vector fields on $X$.

@@

Notice that the Beltrami differential $\mu^{\Bar{i}}_j \d \zbar_{\Bar{i}} \otimes \del_z$ as well as the components of the three-form which survive the minimal twist sit inside as odd sections of this sheaf of $L_\infty$ algebras.

@@

In the works \cite{CostelloM5,CostelloM2} Costello has introduced a program to analyze holography for membranes and fivebranes in the $\Omega$-deformation of the nonminimal twist defined on multi Taub--NUT spaces.
The $\Omega$-deformation of the nonminimal twist of the eleven dimensional supergravity was constructed directly from the physical theory and was argued to admit a description in terms of a holomorphic-topological gauge theory in five dimensions.

@@

There are two parameters in this theory which Costello calls $\delta$ and $\ep$.
The parameter $\delta$ controls the Chern--Simons type coupling, which in this section and going forward we will simply set to be the unit. 
The parameter $\ep$ measures the non-commutativity. 
It appears through the formal deformation quantization of~$Y$ which is the associative algebra $\cO(Y)[[\ep]]$ equipped with the Moyal product $\star$.

We consider the following subalgebra of complex-valued forms on $S\times Y$:
\[
\cL_{5d} \define \oplus_{k,q}\Omega^{k}(S)\hotimes \Omega^{0,q}(Y) \subset \Omega^\bu(S \times Y) .
\]
We continue to label elements of the homogeneous pieces as $(k;q)$ forms.
We will use the notation $\alpha^{k;q}$ with $k+q=$ for the corresponding homogenous components.
Not only is $\cL_{5d}$ a dg algebra, if we adjoin formal parameter then $\cL_{5d}[[\ep]]$ is a dg Lie algebra with respect to the Moyal commutator $[-,-]_\star$.

@@

We can take a gauge condition where $\alpha^{1;0}$ vanishes.
In this case the equations of motion for the one-form field simply reads
\beqn
\dbar \alpha^{0;1} + \alpha^{0;1} \star \alpha^{0;1} = 0,
\eeqn
together with the condition that $\d_S \alpha^{0;1} = 0$.
Here $\star$ denotes the holomorphic Moyal product on $Y$ and $\d$, $\dbar$ denote the de Rham and Dolbeault differentials along $S$,$Y$ respectively.

@@

Gauge symmetries are given by degree $-1$ elements in $\cL_{5d}[[\ep]][1]$ which are simply functions $\alpha^{0;0} \in C^\infty (S\times Y)[[\ep]]$. 
Explicitly, the corresponding infinitesimal gauge transformation is given in components by
\[
\alpha^{k;q}\mapsto \alpha^{k;q} + \d_S \alpha^{0;0} +\dbar \alpha^{0;0} + \{\alpha^{0;0}, \alpha^{k;q}\}_{Y}
\]

The full BV action functional describing this model is the non-commutative Chern--Simons action
\beqn
S(\alpha) = \int_{S \times Y} \left(\frac12 \alpha \d \alpha + \frac13 \alpha \star \alpha \star \alpha \right) \wedge \Omega_Y .
\eeqn
Here, $\alpha$ represents an arbitrary element of $\cL_{5d}[[\ep]]$ and $\d$ is the full de Rham differential on $S \times Y$.

@@

It is expected that the worldvolume theory of fivebranes in $M$-theory on flat space is equipped with $\cN=(2,0)$ superconformal symmetry. 
Six-dimensional $\cN=(2,0)$ supersymmetry admits two inequivalent classes of twists characterized by the number of directions which are left invariant:
\begin{itemize}
\item 
The holomorphic, or minimal, twist. 
This twist leaves three real directions invariant. 
The holomorphic twist of any $\cN=(2,0)$ theory can be defined on any complex three-fold $Z$ equipped with a square-root of its canonical bundle. 
\item 
The non-minimal twist. 
This twist leaves five real directions invariant.
The non-minimal twist of any $\cN=(2,0)$ theory can be defined on a six-manifold of the form $M^4 \times \Sigma$ where $M^4$ is a smooth four-manifold and $\Sigma$ is a Riemann surface. 
\end{itemize}

@@

This theory notoriously does not admit a Lagrangian description. 
However, it can still be put in a degenerate form of the BV formalism where the space of fields above is equipped with an odd Poisson bivector \cite{SWtensor}.
We describe this Poisson bivector explicitly
\surya{ FINISH }
In the (degenerate) BV formalism, this free theory can be packaged into the data of an abelian $\Z \times \Z/2$ graded local Lie algebra on $Z$ which is of the form 
\[
\cL_{N=1} = \Omega^{\geq 2, \bu}(Z) \oplus \Pi \Omega^{0,\bu}(Z, K^{1/2}_Z) \otimes \C^2 .
\]

@@

The theory on a stack of $N$ membranes probing the origin in $\C^{4}/\Z_{k}$ is expected to be described by the ABJM theory - a 3d $\cN=6$ superconformal gauge theory with gauge group $U(N)\times U(N)$ at levels $\pm k$ respectively \cite{} For $k=1,2$ the theory witnesses an enhancement to $\cN=8$ due to a nonperturbative effect. \cite{}

Twists of $\cN=8$ gauge theories in 3d were classified in \cite{}. Moreover, the ABJM theories are examples of 3d $\cN=2$ Chern-Simons matter theories, whose twists were studied in \cite{}. Twists of such occur in two inequivalent classes, similarly labeled by the dimension of the subspace of translations given by the image of the twisting supercharge:

\begin{itemize}
  \item The minimal twist. This twist leaves 2 real directions invariant. The theory can be defined on a 3-manifold of the form $S\times \Sigma$ where $S$ is a smooth oriented one-manifold and $\Sigma$ is a Riemann surface equipped with a fourth-root of its canonical bundle.

@@

We briefly recall the description of the minimal twist of the ABJM theory for $N=1$.

\surya{fields, gauge symmetries, etc}

In the BV formalism, this free theory can be packaged into the data of an abelian $\Z$ graded local Lie algebra on $\Sigma$ which takes the form
\[
\Omega^{\bu}(S)\times \left (\Omega^{0,\bu}(\Sigma) \oplus \Pi \Omega^{0,\bu} (\Sigma )\right ) \otimes \C^{4}.
\]

>>>>

%\documentclass[11pt]{amsart}%
%
%%\usepackage{../macros-master}
%\usepackage{macros-fivebrane}

%
%\begin{document}
%

\section{Twists in dimensions eleven, six, and three}
\label{s:twisted}

In this section we review the descriptions of twists of the key players in $M$-theory including eleven-dimensional supergravity as well as the three and six-dimensional superconformal field theories associated to the abelian Lie algebra~$\lie{gl}(1)$.

@@

Eleven-dimensional supersymmetry admits two inequivalent classes of twists characterized by the dimension of the subspace of translations spanned by the image of bracketing with the twisting supercharge.
\begin{itemize}
\item 
The minimal twist. 
This twist leaves six real directions invariant and is preserved by the subgroup $SU(5)$ of the Lorentz group. 
\item 
The non-minimal twist. 
This twist leaves nine real directions invariant and is preserved by the subgroup $SU(2) \times G_2$ of the Lorentz group. 
\end{itemize}

@@

The eleven-dimensional theory described in \cite{RSW} exists on any manifold which is locally of the form 
\[
S \times X 
\] 
where $X$ is a Calabi--Yau fivefold and $S$ is a real oriented smooth one-dimensional manifold.
More generally, the eleven-dimensional theory can be constructed on any eleven-manifold equipped with a transversely holomorphic foliation which is equipped with an appropriate holomorphic volume form on the leaves of the foliation.
We will elaborate on this further in \S \ref{sec:states}.

We recall the fields and equations of motion of this eleven-dimensional theory.

@@

%To begin this section we highlight some of the important features of the eleven-dimensional model considered in \cite{RSW}. 
%Let's first consider the case that the eleven-dimensional manifold is of the form $S \times X$, where $X$ is a Calabi--Yau fivefold.
Let $\T_X$ stand for the holomorphic tangent bundle of the Calabi--Yau fivefold $X$ and $\Bar{\T}_X$ its complex conjugate.
The complexified tangent bundle of the eleven-manifold $S \times X$ decomposes as
\[
\T_S \oplus \T_X \oplus \Bar{\T}_X 
\]
where $\T_S$ is the complexified tangent bundle of the smooth one-manifold $S$.
Locally, we choose coordinates $(t;z,\zbar)$ where $t$ is a smooth coordinate for $S$ and $z$ is a holomorphic coordinate for $X$.

Momentarily we will give a full presentation of the fields and equations of motion within the Batalin--Vilkovisky (BV) formalism.
But first, we will give a more direct description of the equations of motion and gauge symmetries of the model.

One of the primary fields of eleven-dimensional supergravity describes deformations of the metric $g$.
Since we work in a background which has $SU(5)$ holonomy we can take the background metric on $S \times X$ to be the product of the flat metric on $S$ with a Calabi--Yau metric $g_{X}$ on $X$.

Deformations of the background metric which survive the twist can be identified with Beltrami differentials, that is, sections of 
\[
\Bar{\T}_X^* \otimes \T_X \cong \Bar{\T}^*_X \otimes \Bar{\T}_X^* . 
\]
Here, we have used the isomorphism granted by the K\"ahler metric $g_{X}$.
In local holomorphic coordinates $\mu$ admits a description like
\[
\mu^{\Bar{i}}_j (t;z,\zbar) \d \zbar_{\Bar{i}} \otimes \del_{z_j} .
\]
More generally, the fields of this model include sections of the holomorphic tangent bundle with coefficients in Dolbeault forms on $X$ of arbitrary Dolbeault type and de Rham forms on $S$, which we can write in superfield notation as 
\[
\mu = \mu^{\Bar{I}}_j (t;z,\zbar) \d \zbar_{\Bar{I}} \otimes \del_{z_j} + \mu^{\Bar{I}}_{t,j} (t;z,\zbar) \d t \d \zbar_{\Bar{I}} \otimes \del_{z_j}
\]
where there is a sum over the multi-index $\Bar{I}$ as it ranges over subsets of $\{1,\ldots,5\}$.
In this notation, the component $\mu^{\Bar{I}}_j$ is {\em odd} if $|\Bar{I}|=0,2,4$ is even and {\em even} if $|I| = 1,3,5$ is odd.
Similarly, the component $\mu^{\Bar{I}}_{t,j}$ is {\em even} if $|\Bar{I}|=0,2,4$ is even and {\em odd} if $|I| = 1,3,5$ is odd.
In particular we have odd fields $\mu_j(t;z,\zbar) \del_{z_j}$ which play the role of ghosts for infinitesimal changes of coordinates.
We will see that the equations of motion dictate that we only see changes of holomorphic coordinates.

The field $\mu$ satisfies a condition that it be {\em divergence-free} for the Calabi--Yau structure on the fivefold~$X$.
This means that it is required to satisfy the equation
\beqn
\div \mu = 0
\eeqn
where $\div(-)$ is the divergence with respect to the holomorphic volume form $\Omega$ on $X$.
By including the full space of BV fields, this condition does arise from an action functional principle---it is not an additional constraint like the one present in the six-dimensional superconformal theory.
The field to add in this situation is a Dolbeault form $\nu \in \Omega^{0,\bu}(X)$ which imposes the equation above upon setting $\nu = 0$.
Another piece of the equations of motion for~$\mu$ dictate that it be locally constant along~$S$.

@@

The other primary bosonic field of eleven-dimensional supergravity is a three-form.
In the BV formalism we see all types of differential forms corresponding to a tower of ghosts for this higher gauge field together with antifields and antighosts.

On $S \times X$ the space of complex-valued differential forms decomposes into de Rham--Dolbeault forms as in
\[
\oplus_{k,p,q} \Omega^k(S) \otimes \Omega^{p,q}(X) .
\]
We refer to the homogenous pieces as the space of $(k;p,q)$ forms, these admit local presentations as
\[
\sum_{P,Q} f_{PQ} (t;z,\zbar) \d z_P \d \zbar_Q + \sum_{P',Q'} g_{P'Q'}(t;z,\zbar) \d t \d z_{P'}\d \zbar_{Q'} 
\]
where the first sum is over tuples~$P=(p_1,p_2,p_3),Q=(q_1,q_2,q_3)$ and
the second sum is over tuples~$P'=(p'_1,p'_2,p'_3),Q=(q'_1,q'_2,q'_3)$

In the minimal twist only forms with $p_i ,p_i'\leq 1$ survive. 
Thus, we have as part of the complex of fields in the twisted theory the space of forms
\[
\left(\oplus_{k,q} \Omega^k(S) \otimes \Omega^{0,q}(X)\right) \oplus 
\left(\oplus_{k',q'} \Omega^{k'}(S) \otimes \Omega^{1,q'}(X)\right) .
\]
We denote a general (non-homogenous) element in the first summand by $\beta$ and an element in the second summand by $\gamma$.
As above we can expand such fields in local coordinates using multi-indices by 
\begin{align*}
\beta & = \beta^{\Bar{I}} \d \zbar_{\Bar{I}} + \beta_t^{\Bar{J}} \d t \d \zbar_{\Bar{J}}\\
\gamma & = \gamma^{i \Bar{I}} \d z_i \d \zbar_{\Bar{I}} + \gamma_t^{j \Bar{J}} \d t \d z_j \d \zbar_{\Bar{J}}.
\end{align*}
%When we want to be specific by the form type we use the notation $\beta^{k;q}(t;z,\zbar)$ for the $(k;0,q)$ component of the three-form and $\gamma^{k;q}(t;z,\zbar)$ for the $(k;1,q)$ component of the three-form.
Fields $\beta^{\Bar{I}}, \gamma_t^{i \Bar{I}}$ with $|\Bar{I}| = $odd (resp. even) are {\em even} (resp. {\em odd}) and fields $\beta_t^{\Bar{I}}, \gamma^{i \Bar{I}}$ with $|\Bar{I}| = $odd (resp. even) are {\em odd} (resp. {\em even}).

The most important equation of motion of the eleven-dimensional theory involves both the fields $\mu$ and $\gamma$. 
When $\div \mu = 0$ it takes the form
\beqn\label{eqn:eom2}
\dbar \mu + \frac12 [\mu,\mu] = \del \gamma \del \gamma .
\eeqn
Because of the term on the right hand side this equation is not exactly the usual Beltrami equation for deformations of complex structures.
On the left hand side we are implicitly using an identification between the holomorphic tangent bundle $\T_X$ and the bundle $\wedge^4 \T^*_X$ granted by the holomorphic volume form on $X$.
This allows us to view this equation as taking place entirely in the graded space $\Omega^\bu(S) \hotimes \Omega^{4,\bu}(X)$. 
In particular, this equation is inhomogenous in form type.
As an example of the homogenous form type $(0;4,2)$ piece of this equation we have 
\[
\ep^{ijklm} \del_{\zbar_{\bar{j}}} \mu_m^{\bar{i}} + \ep^{ijkmn} \del_{z_l} (\mu_{m} \mu_{n}) =\del_{z_i} \gamma^{j \bar{i}} \del_{z_k} \gamma^{l \bar{j}} 
\]

%Along $S$, $\beta$ and $\gamma$ behave like abelian gauge fields.
%Thus, locally we can assume that the $\Omega^1(S)$ components are exact and the $\Omega^0(S)$ components are locally constant.

@@

We move on to give a complete description of our eleven-dimensional model within the Batalin--Vilkovisky (BV) formalism.
In the superfield notation above we have implicitly provided all components of the ghosts, fields, anti-fields, and anti-ghosts.
One of the key structures in the BV formalism is the graded skew-symmetric pairing between fields and antifields (ghosts and antighosts).
Once such a pairing $\omega_{BV}$ is introduced, one can opt to describe solutions to the equations of motion as Maurer--Cartan elements of a certain sheaf of ($\Z/2$-graded) $L_\infty$ algebras on $X \times S$.

@@

The $L_\infty$ structure on the sheaf of holomorphic sections of $L_X$ is described as follows. 
First, $\d = [-]_1$, the differential, is simply given by 
\begin{align*}
\d \beta & = \del \beta \in \Omega^1_X \subset L_{X,-} \\
\d \mu & = \div \mu \in \cO_{X,\nu} \subset L_{X, -}
\end{align*}
and $\d \gamma = \d \nu = 0$. 
For $k \geq 2$ the general formula for the $k$-ary brackets is 
\begin{align*}
[\nu_1, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \div(\nu_1 \cdots \nu_k \mu_1 \wedge \mu_2) \in \PV^1_X \\
[\nu_1,\ldots, \nu_{k-3}, \mu_1,\mu_2,\gamma]_k & = \nu_1 \cdots \nu_{k-3} (\mu \wedge \mu') \vee \del \gamma \in \cO_{X,\beta} .\\
[\nu_1,\ldots,\nu_{k-2}, \mu, \gamma]_k & = \nu_1 \cdots \nu_{k-2} \mu \vee \del \gamma \in \Omega^1_X \\
[\gamma_1,\gamma_2] & = \Omega_X \vee (\del \gamma_1 \wedge \del \gamma_2) \in \PV^1_X .
\end{align*}
In \cite{RSW} it is shown that this endows $L_{X}$ with the structure of a sheaf of $\Z/2$ graded $L_\infty$ algebras.
There is a sub sheaf given by the sections $\mu$ and $\nu$ which is $L_\infty$-equivalent to the sheaf of holomorphic divergence-free vector fields on $X$.

@@

The free part of the BV action is easy to describe
\beqn
\int_{S \times X} \left(\gamma \d \mu\right) \Omega_X + \int_{S \times X} (\beta \dbar \nu) \Omega_X + \int_{S \times X} (\beta \div \mu) \Omega_X ,
\eeqn
where $\Omega_X$ is the holomorphic volume form on~$X$.
Notice that in the first two terms no holomorphic derivatives appear in the direction of $X$ due to the presence of this holomorphic volume form.

The interacting part of the action is more complicated, partly for the reason that in our presentation above it is given by a formal series in the space of fields, rather than just a polynomial in the fields. 
Explicitly, the interaction can be written as
\beqn
\frac12 \int_{S \times X} (\mu^2 \del \gamma) \frac{\Omega_X}{1- \nu} + \frac16 \int_{S \times X} \gamma \del \gamma \del \gamma .
\eeqn
%
%Notice that the Beltrami differential $\mu^{\Bar{i}}_j \d \zbar_{\Bar{i}} \otimes \del_z$ as well as the components of the three-form which survive the minimal twist sit inside as odd sections of this sheaf of $L_\infty$ algebras.

@@

In the works \cite{CostelloM5,CostelloM2} Costello has introduced a program to analyze holography for membranes and fivebranes in the $\Omega$-deformation of nonminimally twisted supergravity defined on multi Taub--NUT spaces.
The $\Omega$-deformation of the nonminimal twist of eleven dimensional supergravity was constructed directly from the physical theory and was argued to admit a description in terms of a holomorphic-topological gauge theory in five dimensions.

@@

There are two parameters in this theory $\delta$ and $\ep$, see \textit{loc. cit.}.
The parameter $\delta$ controls the coupling of the Chern--Simons action, which in this section and going forward we will simply set to be the unit. 
The parameter $\ep$ measures the non-commutativity---
it appears through the formal deformation quantization of~$Y$ which is the associative algebra $\cO(Y)[[\ep]]$ equipped with the Moyal product $\star_\ep$.

We consider the following subalgebra of complex-valued forms on $S\times Y$:
\[
\cL_{5d} \define \oplus_{k,q}\Omega^{k}(S)\hotimes \Omega^{0,q}(Y) \subset \Omega^\bu(S \times Y) .
\]
In local coordinates a general differential form in $\cL_{5d}$ admits a decomposition as
\[
\alpha = \alpha^{\Bar I} \d \zbar_{\Bar I} + \alpha^{\Bar I}_t \d t \d \zbar_{\Bar I} .
\]
%We will use the notation $\alpha^{k;q}$ with $k+q=$ for the corresponding homogenous components.
We can understand the Moyal product along the holomorphic symplectic surface $Y$ as endowing $\cL_{5d}[[\ep]]$ with the structure of a dg algebra. 
Of course, we can forget down to a dg Lie algebra structure with respect to the Moyal commutator $[-,-]_{\star_{\ep}}$.

@@

We can take a gauge condition where the $\d t$ component of the one-form $\alpha_t$ vanishes.
In this case the equations of motion for the one-form field, in components, simply reads
\beqn
\del_{\zbar_{\Bar{i}}} \alpha^{\Bar{j}} + \alpha^{\Bar{i}} \star_\ep \alpha^{\Bar{j}} = 0,
\eeqn
together with the condition that $\del_t \alpha^{\Bar{i}} = 0$ for all $\Bar{i}, \Bar{j}$.
%Here $\star_{\ep}$ denotes the holomorphic Moyal product on $Y$ and $\del_t$, $$ denote the de Rham and Dolbeault differentials along $S$,$Y$ respectively.

@@

Gauge symmetries are given by degree $-1$ elements in $\cL_{5d}[[\ep]][1]$ which are simply functions $f \in C^\infty (S\times Y)[[\ep]]$. 
Explicitly, the corresponding infinitesimal gauge transformation for the one-form component of $\alpha$ is given by
\[
\alpha \mapsto \alpha + \del_t f \d t +\del_{\zbar_{\Bar{i}}} f \d \zbar_{\Bar{i}} + [f, \alpha]_{\star_\ep} .
\]
Here, $[-,-]_{\star_{\ep}}$ is the commutator with respect to the Moyal product $\star_\ep$.

The full BV action functional describing this model is the non-commutative Chern--Simons action
\beqn
S(\alpha) = \int_{S \times Y} \left(\frac12 \alpha \d \alpha + \frac13 \alpha \star_\ep \alpha \star_\ep \alpha \right) \wedge \Omega_Y .
\eeqn
Here, $\alpha$ represents an arbitrary element of $\cL_{5d}[[\ep]]$ and $\d$ is the full de Rham differential on $S \times Y$ (notice that that no holomorphic derivatives appear in the kinetic term due to the appearance of $\Omega_Y$).

@@

It is expected that the worldvolume theory of fivebranes in $M$-theory on flat space is equipped with $\cN=(2,0)$ superconformal symmetry. 
Six-dimensional $\cN=(2,0)$ supersymmetry admits two inequivalent classes of twists characterized by the number of directions which are left invariant:
\begin{itemize}
\item 
The holomorphic, or minimal, twist. 
This twist leaves three real directions invariant and is stabilized by the double cover of the group $U(3)$. 
The holomorphic twist of any $\cN=(2,0)$ theory can be defined on any complex three-fold $Z$ equipped with a square-root of its canonical bundle. 
\item 
The non-minimal twist. 
This twist leaves five real directions invariant and is stabilized by the group $SO(4) \times U(1)$. 
The non-minimal twist of any $\cN=(2,0)$ theory can be defined on a six-manifold of the form $M^4 \times \Sigma$ where $M^4$ is a smooth four-manifold and $\Sigma$ is a Riemann surface. 
\end{itemize}

@@

This theory notoriously does not admit a Lagrangian description. 
However, it can still be put in a degenerate form of the BV formalism where the space of fields above is equipped with an odd Poisson bivector \cite{SWtensor}.
In the (degenerate) BV formalism, the space of fields of the theory is
\beqn
\cE^{6d}_{\lie{u}(1)} = \Omega^{\geq 2, \bu}(Z)[1] \oplus \Pi \Omega^{0,\bu}(Z, K^{1/2}_Z) \otimes \C^2 [1] ,
\eeqn
and the linear BRST differential is described by the following diagram
\beqn\label{eqn:weight-1a}
\begin{tikzcd}
\ul{-1} & \ul{0}\\
\Pi \Omega^{0,\bu}(Z, K_Z^{1/2} \otimes \C^2) & \\
\Omega^{2,\bu}(Z) \ar[r,"\del"] & \Omega^{3,\bu}(Z) ,
\end{tikzcd}
\eeqn
where the $\dbar$ operator acts implicitly on each summand.

@@

The theory on a stack of $N$ membranes probing the origin in $\C^{4}/\Z_{k}$ is expected to be described by the ABJM theory---a 3d $\cN=6$ superconformal gauge theory with gauge group $U(N)\times U(N)$ at levels $\pm k$ respectively \cite{Aharony:2008ug}. 
For $k=1,2$ the theory witnesses an enhancement to $\cN=8$ due to a nonperturbative effect \cite{Bagger:2007jr,Gustavsson:2007vu}.

Twists of three-dimensional $\cN=8$ supersymmetric gauge theories were classified and characterized in \cite{ESsusy,ESW,Garner:2022vds}. 
Moreover, the ABJM theories are examples of 3d $\cN=2$ Chern-Simons matter theories, whose twists were studied in \cite{Aganagic:2017tvx}. 
Twists of such occur in two inequivalent classes, similarly labeled by the dimension of the subspace of translations given by the image of the twisting supercharge:

\begin{itemize}
  \item The minimal twist. This twist leaves 2 real directions invariant. The theory can be defined on a 3-manifold of the form $S\times C$ where $S$ is a smooth oriented one-manifold and $C$ is a Riemann surface equipped with a fourth-root of its canonical bundle.

@@

We briefly recall the description of the minimal twist of the ABJM theory associated to the single membrane theory.
Let $K^{1/4}_C$ be a fourth-root of the canonical bundle of $C$. 
In the BV formalism, this free theory has underlying space of fields
\[
\Omega^{\bu}(S) \hotimes \left[ \Omega^{0,\bu}(C, K^{1/4}_C \otimes \C^4) \oplus \Pi \Omega^{0,\bu} (C,K^{3/4}_C \otimes \C^4) \right] .
\]
The linear BRST differential is of the form $\d_{S} + \dbar_C$ where $\d_S$ is the de Rham differential along $S$ and $\dbar_C$ is the anti-holomorphic Dolbeault operator along $\Sigma$.
If we split the fields according to the direct sum above by $X, \Psi$ then the action is simply
\[
\int_{S \times C} \Psi \d_S X + \int_{S \times C} \Psi \dbar_\Sigma X .
\]
Here, we have implicitly chosen a non-degenerate symmetric pairing on $\C^4$.
